---
title: "Markers expression and clinical features"
---
```{r global, message=FALSE, warning=FALSE, echo=FALSE}
source("global.R")

# Filtering out rows with normal urotheliu or carcinoma in situ
DF <- DF_ASSOCIATION %>% 
    filter(
        dx_final != "Normal urothelium",
        dx_final != "Carcinoma in situ"
    )

# Removing the row for case S07-42476 corresponding to HG
# Removal was done due to the fact that the case had 2 rows, one with UC and the other with HG, and only UC was required for analysis
DF <- DF[-73 , ]
```

In this section, we analyze the association between markers extent (i.e., percentage of "positive" cells) and clinical features. First, we grouped all TMA spots by SP number. We then summarized the markers expression using the median value across all TMA spots for that case and diagnosis. If a case had more than one type of lession, we used only the highest grade/stage lession. Thus, each row in the dataset corresponded to the median value of the markers expression for that instance.

Patient's age was categorized in younger vs. older using the median age as the cutoff point. We compared the (summarized) markers expression by clinical features using boxplots and density plots. For statistical testing, we used the Mann-Whitney U test or the Kruskal-Wallis rank sum test, depending on the number of levels of the grouping variable.

***

# **CK5/6 expression**
## Patient's age group
```{r age_group.ck56_median}
x <- DF$ck56_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.ck56_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.ck56_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **CK20 expression**
## Patient's age group
```{r age_group.ck20_median}
x <- DF$ck20_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.ck20_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.ck20_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **CD44 expression**
## Patient's age group
```{r age_group.cd44_median}
x <- DF$cd44_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.cd44_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.cd44_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **p53 expression**
## Patient's age group
```{r age_group.p53_median}
x <- DF$p53_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.p53_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.p53_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **GATA3 expression**
## Patient's age group
```{r age_group.gata3_median}
x <- DF$gata3_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.gata3_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.gata3_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **ER expression**
## Patient's age group
```{r age_group.er_median}
x <- DF$er_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.er_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.er_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **Ki67 expression**
## Patient's age group
```{r age_group.ki67_median}
x <- DF$ki67_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.ki67_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.ki67_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **HER2 expression**
## Patient's age group
```{r age_group.her2_median}
x <- DF$her2_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.her2_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.her2_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **Uroplakin expression**
## Patient's age group
```{r age_group.uroplakin_median}
x <- DF$uroplakin_median
y <- DF$age_group
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's sex
```{r gender.uroplakin_median}
y <- DF$gender
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Patient's race
```{r race.uroplakin_median}
y <- DF$race
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***
