---
title: "Markers expression by pathologic features"
---

```{r global, message=FALSE, warning=FALSE, echo=FALSE}
source("global.R")

DF <- DF_ASSOCIATION

```

In this section, we analyze the association between markers extent (i.e., percentage of "positive" cells) and pathologic features. First, we grouped all TMA spots by SP number and pathologic diagnosis. We then summarized the markers expression using the median value across all TMA spots for that case and diagnosis. We finally included the highest grade/stage lession for each case (v.g., if a case had normal urothelium, low-grade noninvasive papillary urothelial carcinoma, and invasive urothelial carcinoma, we only kept the instances corresponding to the urothelial carcinoma). Thus, each row in the dataset corresponded to the median value of the markers expression measured in the highest grade/stage lession.

***

# **CK5/6 expression**
## pT
```{r pt.ck56_median}
x <- DF$ck56_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.ck56_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.ck56_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.ck56_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.ck56_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **CK20 expression**
## pT
```{r pt.ck20_median}
x <- DF$ck20_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.ck20_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.ck20_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.ck20_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.ck206_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **CD44 expression**
## pT
```{r pt.cd44_median}
x <- DF$cd44_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.cd44_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.cd44_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.cd44_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.cd44_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **p53 expression**
## pT
```{r pt.p53_median}
x <- DF$p53_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.p53_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.p53_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.p53_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.p53_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **GATA3 expression**
## pT
```{r pt.gata3_median}
x <- DF$gata3_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.gata3_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.gata3_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.gata3_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.gata3_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **ER expression**
## pT
```{r pt.er_median}
x <- DF$er_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.er_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.er_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.er_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.er_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **Ki67 expression**
## pT
```{r pt.ki67_median}
x <- DF$ki67_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.ki67_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.ki67_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.ki67_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.ki67_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **HER2 expression**
## pT
```{r pt.her2_median}
x <- DF$her2_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.her2_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.her2_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.her2_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.her2_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **Uroplakin expression**
## pT
```{r pt.uroplakin_median}
x <- DF$uroplakin_median
y <- DF$pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Pathologic stage
```{r stage_pt.uroplakin_median}
y <- DF$stage_pt
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Histologic grade
```{r grade.uroplakin_median}
y <- DF$grade
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphovascular invasion
```{r lvi.uroplakin_median}
y <- DF$lvi
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Lymphnodes metastasis
```{r lymphnodes_metastasis.uroplakin_median}
y <- DF$lymphnodes_metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***
