---
title: "Markers expression by diagnosis"
---

```{r global, warning = FALSE, message = FALSE, echo = FALSE}
source("global.R")

# Curating the dataset
DF <- DF_ASSOCIATION

# Defining the grouping variable
y <- DF$dx_final
```

In this section, we analize the markers expression by pathologic diagnosis. For the analysis, we first grouped all the values from each TMA considering SP number and pathologic diagnosis. We then summarized each instance using the median value of the marker extent (i.e., percentage of "positive" cells) accross the TMAs corresponding to this particular instance. We used the median value instead of the mean value due to the marked right skewness we observed in the distribution of the markers extent. Finally, we compared the (summarized) markers expression by pathologic diagnosis using boxplots and density plots. For statistical testing, we used the Kruskal-Wallis rank sum test.

- NU = Normal urothelium
- CIS = Carcinoma *in situ*
- LG = Low-grade noninvasive papillary urothelial carcinoma
- HG = High-grade noninvasive papillary urothelial carcinoma
- UC = Urothelial carcinoma

***

## **CK5/6 expression**
```{r histology_ck56}
x <- DF$ck56_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **CK20 expression**
```{r histology_ck20}
x <- DF$ck20_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **CD44 expression**
```{r histology_cd44}
x <- DF$cd44_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **p53 expression**
```{r histology_p53}
x <- DF$p53_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **GATA3 expression**
```{r histology_gata3}
x <- DF$gata3_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **ER expression**
```{r histology_er}
x <- DF$er_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **Ki67 expression**
```{r histology_ki67}
x <- DF$ki67_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **HER2 expression**
```{r histology_her2}
x <- DF$her2_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## **Uroplakin expression**
```{r histology_uroplakin}
x <- DF$uroplakin_median
tbl_nice(x, y)
tbl_kw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***
