---
title: "Markers expression and outcome features"
---

```{r global, message=FALSE, warning=FALSE, echo=FALSE}
source("global.R")

# Filtering out rows with normal urotheliu or carcinoma in situ
DF <- DF_ASSOCIATION %>% 
    filter(
        dx_final != "Normal urothelium",
        dx_final != "Carcinoma in situ"
    )

# Removing the row for case S07-42476 corresponding to HG
# Removal was done due to the fact that the case had 2 rows, one with UC and the other with HG, and only UC was required for analysis
DF <- DF[-73 , ]
```

In this section, we analyze the association between markers extent (i.e., percentage of "positive" cells) and outcome features. First, we grouped all TMA spots by SP number and pathologic diagnosis. We then summarized the markers expression using the median value across all TMA spots for that case and diagnosis. We finally included the highest grade/stage lession for each case (v.g., if a case had normal urothelium, low-grade noninvasive papillary urothelial carcinoma, and invasive urothelial carcinoma, we only kept the instances corresponding to the urothelial carcinoma). Thus, each row in the dataset corresponded to the median value of the markers expression measured in the highest grade/stage lession.

We compared the (summarized) markers expression by outcome features using boxplots and density plots. For statistical testing, we used the Mann-Whitney U test or the Kruskal-Wallis rank sum test, depending on the number of levels of the grouping variable.

***

# **CK5/6 expression**
## Distant metastasis
```{r metastasis.ck56_median}
x <- DF$ck56_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.ck56_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.ck56_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.ck56_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **CK20 expression**
## Distant metastasis
```{r metastasis.ck20_median}
x <- DF$ck20_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.ck20_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.ck20_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.ck20_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **CD44 expression**
## Distant metastasis
```{r metastasis.cd44_median}
x <- DF$cd44_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.cd44_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.cd44_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.cd44_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **p53 expression**
## Distant metastasis
```{r metastasis.p53_median}
x <- DF$p53_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.p53_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.p53_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.p53_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **GATA3 expression**
## Distant metastasis
```{r metastasis.gata3_median}
x <- DF$gata3_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.gata3_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.gata3_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.gata3_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **ER expression**
## Distant metastasis
```{r metastasis.er_median}
x <- DF$er_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.er_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.er_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.er_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **Ki67 expression**
## Distant metastasis
```{r metastasis.ki67_median}
x <- DF$ki67_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.ki67_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.ki67_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.ki67_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **HER2 expression**
## Distant metastasis
```{r metastasis.her2_median}
x <- DF$her2_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.her2_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.her2_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.her2_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

# **Uroplakin expression**
## Distant metastasis
```{r metastasis.uroplakin_median}
x <- DF$uroplakin_median
y <- DF$metastasis
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Tumor progression
```{r progression.uroplakin_median}
y <- DF$progression
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Overall mortality
```{r dead.uroplakin_median}
y <- DF$dead
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***

## Cancer-related mortality
```{r dod.uroplakin_median}
y <- DF$dod
tbl_nice(x, y)
tbl_mw(x, y)
g2_boxplot(x, y)
g2_density(x, y)
```

***
