---
title: "Markers Features"
---

```{r global, warning = FALSE, message = FALSE, echo = FALSE}
source("global.R")
DF <- DF_MARKERS
```

In this section, we describe the expression features of the analyzed markers, including extent (i.e., percentage) of "positive" cells, expression patterns, and expression intensity, as observed in the TMA spots. Thus, the values reported here correspond to the overall features of the markers across all TMA spots. The dataset included `r nrow(DF)` TMA spots.

***

## **CK5/6 expression**
### Percentage of positive cells
```{r ck56_extent}
x <- DF$ck56_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern
```{r ck56_pattern}
x <- DF$ck56_pattern
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r ck56_intensity}
x <- DF$ck56_intensity
tbl_nice(x)
g_barplot(x)
```

***

## **CK20 expression**
### Percentage of positive cells
```{r ck20_extent}
x <- DF$ck20_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern
```{r ck20_pattern}
x <- DF$ck20_pattern
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r ck20_intensity}
x <- DF$ck20_intensity
tbl_nice(x)
g_barplot(x)
```

***

## **CD44 expression**
### Percentage of positive cells
```{r cd44_extent}
x <- DF$cd44_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern (#1)
```{r cd44_pattern_1}
x <- DF$cd44_pattern_1
tbl_nice(x)
g_barplot(x)
```

***

### Expression pattern (#2)
```{r cd44_pattern_2}
x <- DF$cd44_pattern_2
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r cd44_intensity}
x <- DF$cd44_intensity
tbl_nice(x)
g_barplot(x)
```

***

## **p53 expression**
### Percentage of positive cells
```{r p53_extent}
x <- DF$p53_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern (#1)
```{r p53_pattern_1}
x <- DF$p53_pattern_1
tbl_nice(x)
g_barplot(x)
```

***

### Expression pattern (#2)
```{r p53_pattern_2}
x <- DF$p53_pattern_2
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r p53_intensity}
x <- DF$p53_intensity
tbl_nice(x)
g_barplot(x)
```

***

## **GATA3 expression**
### Percentage of positive cells
```{r gata3_extent}
x <- DF$gata3_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern (#1)
```{r gata3_pattern_1}
x <- DF$gata3_pattern_1
tbl_nice(x)
g_barplot(x)
```

***

### Expression pattern (#2)
```{r gata3_pattern_2}
x <- DF$gata3_pattern_2
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r gata3_intensity}
x <- DF$gata3_intensity
tbl_nice(x)
g_barplot(x)
```

***

## **ER expression**
### Percentage of positive cells
```{r er_extent}
x <- DF$er_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern (#1)
```{r er_pattern_1}
x <- DF$er_pattern_1
tbl_nice(x)
g_barplot(x)
```

***

### Expression pattern (#2)
```{r er_pattern_2}
x <- DF$er_pattern_2
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r er_intensity}
x <- DF$er_intensity
tbl_nice(x)
g_barplot(x)
```

***

## **Ki67 expression**
### Percentage of positive cells
```{r ki67_extent}
x <- DF$ki67_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

## **HER2 expression**
### Percentage of positive cells
```{r her2_extent}
x <- DF$her2_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern
```{r her2_pattern}
x <- DF$her2_pattern
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r her2_intensity}
x <- DF$her2_intensity
tbl_nice(x)
g_barplot(x)
```

***

### Expression using the breast system
```{r her2_brst}
x <- DF$her2_brst
tbl_nice(x)
g_barplot(x)
```

***

### Expression using the stomach system
```{r her2_stmch}
x <- DF$her2_stmch
tbl_nice(x)
g_barplot(x)
```

***

## **Uroplakin expression**
### Percentage of positive cells
```{r uroplakin_extent}
x <- DF$uroplakin_extent
tbl_nice(x)
g_histogram(x, bin = 10)
g_density(x)
```

***

### Expression pattern (#1)
```{r uroplakin_pattern_1}
x <- DF$uroplakin_pattern_1
tbl_nice(x)
g_barplot(x)
```

***

### Expression pattern (#2)
```{r uroplakin_pattern_2}
x <- DF$uroplakin_pattern_2
tbl_nice(x)
g_barplot(x)
```

***

### Expression intensity
```{r uroplakin_intensity}
x <- DF$uroplakin_intensity
tbl_nice(x)
g_barplot(x)
```

***
