---
title: "Cohort features"
---

```{r global, echo = FALSE, message = FALSE, warning = FALSE}
source("global.R")
```

In this section, we describe the clinical, preoperative, pathologic, treatment, and outcome features of the patients' cohort. Features were described using measures of central tendency and dispersion, histograms, density plots, and barplots. The dataset was composed of `r nrow(DF_FU)` patients.

***

## **Clinical features**
### Age, in years
```{r age}
x <- DF_FU$age
tbl_nice(x)
g_histogram(x, max_break = 90)
g_density(x)
```

***

### Sex
```{r sex}
x <- DF_FU$gender
tbl_nice(x)
g_barplot(x)
```

***

### Race
```{r race}
x <- DF_FU$race
tbl_nice(x)
g_barplot(x)
```

***

### History of prostate cancer
```{r prostate_cancer}
x <- DF_FU$prostate_cancer
tbl_nice(x)
g_barplot(x)
```

***

## **Preoperative features**
### Preoperative procedure
```{r preop_procedure}
x <- DF_FU$preop_procedure
tbl_nice(x)
g_barplot(x)
```

***

### Preoperative carcinoma *in situ*
```{r preop_cis}
x <- DF_FU$preop_cis
tbl_nice(x)
g_barplot(x)
```

***

### Preoperative cT
```{r preop_stage}
x <- DF_FU$preop_stage
tbl_nice(x)
g_barplot(x)
```

***

### Preoperative stage
```{r stage_clinical}
x <- DF_FU$stage_clinical
tbl_nice(x)
g_barplot(x)
```

***

## **Pathologic features**
### pT
```{r pt}
x <- DF_FU$pt
tbl_nice(x)
g_barplot(x)
```

***

### Pathologic stage
```{r stage_pt}
x <- DF_FU$stage_pt
tbl_nice(x)
g_barplot(x)
```

***

### Histologic grade
```{r grade}
x <- DF_FU$grade
tbl_nice(x)
g_barplot(x)
```

***

### Presence of carcinoma *in situ*
```{r cis}
x <- DF_FU$cis
tbl_nice(x)
g_barplot(x)
```

***

### Presence of lymphovascular invasion
```{r lvi}
x <- DF_FU$lvi
tbl_nice(x)
g_barplot(x)
```

***

### Presence of lymph nodes metastasis
```{r lymphnodes_metastasis}
x <- DF_FU$lymphnodes_metastasis
tbl_nice(x)
g_barplot(x)
```

***

## **Treatment features**
### Preoperative radiotherapy
```{r preop_radiotherapy}
x <- DF_FU$preop_radiotherapy
tbl_nice(x)
g_barplot(x)
```

***

### Preoperative chemotherapy
```{r preop_chemotherapy}
x <- DF_FU$preop_chemotherapy
tbl_nice(x)
g_barplot(x)
```

***

### Intravesical chemotherapy
```{r intravesical_chemotherapy}
x <- DF_FU$intravesical_chemotherapy
tbl_nice(x)
g_barplot(x)
```

***

### Type of intravesical chemotherapy
```{r intravesical_chemotherapy_type}
x <- DF_FU$intravesical_chemotherapy_type
tbl_nice(x)
g_barplot(x)
```

***

### Postoperative radiotherapy
```{r postop_radiotherapy}
x <- DF_FU$postop_radiotherapy
tbl_nice(x)
g_barplot(x)
```

***

### Postoperative chemotherapy
```{r postop_chemotherapy}
x <- DF_FU$postop_chemotherapy
tbl_nice(x)
g_barplot(x)
```

***

### Type of postoperative chemotherapy
```{r postop_chemotherapy_type}
x <- DF_FU$postop_chemotherapy_type
tbl_nice(x)
g_barplot(x)
```

***

## **Outcome features**
### Follow-up, in months
```{r fu_months}
x <- DF_FU$fu_months
tbl_nice(x)
g_histogram(x, bin = 24, max_break = 216)
g_density(x)
```

***

### Distant metastasis
```{r metastasis}
x <- DF_FU$metastasis
tbl_nice(x)
g_barplot(x)
```

***

### Tumor progression
```{r progression}
x <- DF_FU$progression
tbl_nice(x)
g_barplot(x)
```

***

### Early complications
```{r complications_early}
x <- DF_FU$complications_early
tbl_nice(x)
g_barplot(x)
```

***

### Late complications
```{r complications_late}
x <- DF_FU$complications_late
tbl_nice(x)
g_barplot(x)
```

***

### Overall mortality
```{r dead}
x <- DF_FU$dead
tbl_nice(x)
g_barplot(x)
```

***

### Cancer-related mortality
```{r dod}
x <- DF_FU$dod
tbl_nice(x)
g_barplot(x)
```

***