---
title: "Survival curves"
---

```{r global, message=FALSE, warning=FALSE, echo=FALSE}
source("global.R")

# Filtering out rows with normal urotheliu or carcinoma in situ
DF <- DF_REGRESSION %>% 
    filter(
        dx_final != "Normal urothelium",
        dx_final != "Carcinoma in situ"
    )

# Removing the row for case S07-42476 corresponding to HG
# Removal was done due to the fact that the case had 2 rows, one with UC and the other with HG, and only UC was required for analysis
DF <- DF[-73 , ]
```

In this section, we plot survival curves for distant metastasis, tumor progression, overall mortality and cancer-related mortality using markers expression. First, we grouped all TMA spots by SP number and pathologic diagnosis. We then summarized the markers expression using the median value across all TMA spots for that case and diagnosis. Next, we included the highest grade/stage lession for each case (v.g., if a case had normal urothelium, low-grade noninvasive papillary urothelial carcinoma, and invasive urothelial carcinoma, we only kept the instances corresponding to the urothelial carcinoma). Thus, each row in the dataset corresponded to the median value of the markers expression measured in the highest grade/stage lession. Finally, we categorized each row as low vs. high expression using the median as the cutoff point.

Survival curves were plotted using the Kaplan-Meier method and they were compared using the log-rank (Mantel-Cox) test.


```{r fu_months}
FU <- DF$fu_months
```


***

# **CK5/6 expression**
## Distant metastasis
```{r metastasis.ck56_group}
status <- DF$ck56_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.ck56_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.ck56_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.ck56_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **CK20 expression**
## Distant metastasis
```{r metastasis.ck20_group}
status <- DF$ck20_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.ck20_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.ck20_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.ck20_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **CD44 expression**
## Distant metastasis
```{r metastasis.cd44_group}
status <- DF$cd44_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.cd44_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.cd44_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.cd44_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **p53 expression**
## Distant metastasis
```{r metastasis.p53_group}
status <- DF$p53_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.p53_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.p53_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.p53_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **GATA3 expression**
## Distant metastasis
```{r metastasis.gata3_group}
status <- DF$gata3_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.gata3_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.gata3_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.gata3_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **ER expression**
## Distant metastasis
```{r metastasis.er_group}
status <- DF$er_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.er_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.er_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.er_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **Ki67 expression**
## Distant metastasis
```{r metastasis.ki67_group}
status <- DF$ki67_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.ki67_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.ki67_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.ki67_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **HER2 expression**
## Distant metastasis
```{r metastasis.her2_group}
status <- DF$her2_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.her2_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.her2_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.her2_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

# **Uroplakin expression**
## Distant metastasis
```{r metastasis.uroplakin_group}
status <- DF$uroplakin_group
outcome <- DF$metastasis
g_surv(FU, outcome, status, ymin = 0.5, x_breaks = 10)
```

***

## Tumor progression
```{r progression.uroplakin_group}
outcome <- DF$progression
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***

## Overall mortality
```{r dead.uroplakin_group}
outcome <- DF$dead
g_surv(FU, outcome, status, x_breaks = 10)
```

***

## Cancer-related mortality
```{r dod.uroplakin_group}
outcome <- DF$dod
g_surv(FU, outcome, status, ymin = 0.3, x_breaks = 10)
```

***
